intro

### 2021-10-29 06_Paper/ER-ED/intro.Rmd
added text on maladaptive ER strategies

[...]
<!-- Als Überleitung: Maladaptive ER Strategien zu ER Flexibility -->
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
This postulation was questioned with the concept of ER flexibility.
*Maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
There was now a greater focus on how ER strategies are being chosen.
For example it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011].  
<!-- Kommentare zu  ER Choice -->
[...]
<!-- Überleitung zu SVs-->
Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

>>>>

[...]
<!-- Als Überleitung: Maladaptive ER Strategien zu ER Flexibility -->
Implications of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between Neurotizism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies with psychological disorders [@Aldao2010].
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
*Maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
To 
For example it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011].  
<!-- Kommentare zu  ER Choice -->
[...]
<!-- Überleitung zu SVs-->
Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].
